Acceleration of plague outbreaks in the second pandemic

### 2022-08-02 supp.Rnw
'in main text'
change I neglected to push on 31 Aug 2020: eqref --> cref in three locations

%% http://tex.stackexchange.com/questions/316510/hyperlink-within-caption-to-a-figure
%% if used in a caption, need short content \caption[...]{ ... \Methodslink ... }
\renewcommand{\Methodslink}{\href[page=8]{ms.pdf}{\emph{Methods}}}

@@

Keeling and Gilligan \cite[p.\,2226]{KeelGill00b} relate the basic
reproduction number to rat density via
%
\begin{linenomath*}
\begin{equation}\label{E:KGR0}
\R_0 = \frac{\beta_{\rm R} K_{\rm F}}{d_{\rm F}}\Big[
1 - \exp{(-aK_{\rm R})} \Big] \,,
\end{equation}
\end{linenomath*}
%
where $\beta$ and $K$ denote transmission rate and carrying capacity, respectively, and the subscripts F and R denote fleas and rats, respectively.  \cref{E:KGR0} implies
%
\begin{linenomath*}
\begin{equation}\label{E:R0ratio}
\frac{\R_{0,2}}{\R_{0,1}} = 
\frac{1 - \exp{(-aK_{{\rm R},2})}}{1 - \exp{(-aK_{{\rm R},1})}} \,,
\end{equation}
\end{linenomath*}
%
which, for $aK_{{\rm R},j}\ll1$, simplifies to
%
\begin{linenomath*}
\begin{equation}\label{E:aKsmall}
\frac{\R_{0,2}}{\R_{0,1}}
\;\approx\; 
\frac{K_{{\rm R},2}}{K_{{\rm R},1}}
\quad.
\end{equation}
\end{linenomath*}
%
The approximation (appropriate in the limit $aK\to0$) provides a lower
bound to the true relationship, indicating that rat density would have
had to increase by at least a factor of \Sexpr{round(R0ratio,2)}
to account for a similar increase \eqref{E:Rratio} in $\R_0$.

\cref{F:KvsR} shows the exact relationship \eqref{E:R0ratio} for
several values of $aK_{{\rm R},1}$, together with the approximation
for small $aK$ \eqref{E:aKsmall}.  Keeling and Gilligan \cite[Table 1,
p.\,2221]{KeelGill00b} adopt values of $a$ and $K_{{\rm R}}$ that
yield $aK_{{\rm R}}=10$.  If this is the correct order of magnitude
for $aK_{{\rm R},1}$ then \cref{E:R0ratio} implies that no increase in
rat density would be sufficient to yield an increase in $\R_0$ by a
factor of \Sexpr{round(R0ratio,2)} (or any factor detectably greater
than 1).

>>>>

%% http://tex.stackexchange.com/questions/316510/hyperlink-within-caption-to-a-figure
%% if used in a caption, need short content \caption[...]{ ... \Methodslink ... }
\renewcommand{\Methodslink}{\href[page=8]{ms.pdf}{\emph{Methods}} in main text}

@@

Keeling and Gilligan \cite[p.\,2226]{KeelGill00b} relate the basic
reproduction number to rat density via
%
\begin{linenomath*}
\begin{equation}\label{E:KGR0}
\R_0 = \frac{\beta_{\rm R} K_{\rm F}}{d_{\rm F}}\Big[
1 - \exp{(-aK_{\rm R})} \Big] \,,
\end{equation}
\end{linenomath*}
%
where $\beta$ and $K$ denote transmission rate and carrying capacity, respectively, and the subscripts F and R denote fleas and rats, respectively.  \cref{E:KGR0} implies
%
\begin{linenomath*}
\begin{equation}\label{E:R0ratio}
\frac{\R_{0,2}}{\R_{0,1}} = 
\frac{1 - \exp{(-aK_{{\rm R},2})}}{1 - \exp{(-aK_{{\rm R},1})}} \,,
\end{equation}
\end{linenomath*}
%
which, for $aK_{{\rm R},j}\ll1$, simplifies to
%
\begin{linenomath*}
\begin{equation}\label{E:aKsmall}
\frac{\R_{0,2}}{\R_{0,1}}
\;\approx\; 
\frac{K_{{\rm R},2}}{K_{{\rm R},1}}
\quad.
\end{equation}
\end{linenomath*}
%
The approximation (appropriate in the limit $aK\to0$) provides a lower
bound to the true relationship, indicating that rat density would have
had to increase by at least a factor of \Sexpr{round(R0ratio,2)}
to account for a similar increase [\cref{E:Rratio}] in $\R_0$.

\cref{F:KvsR} shows the exact relationship [\cref{E:R0ratio}] for
several values of $aK_{{\rm R},1}$, together with the approximation
for small $aK$ [\cref{E:aKsmall}].  Keeling and Gilligan \cite[Table 1,
p.\,2221]{KeelGill00b} adopt values of $a$ and $K_{{\rm R}}$ that
yield $aK_{{\rm R}}=10$.  If this is the correct order of magnitude
for $aK_{{\rm R},1}$ then \cref{E:R0ratio} implies that no increase in
rat density would be sufficient to yield an increase in $\R_0$ by a
factor of \Sexpr{round(R0ratio,2)} (or any factor detectably greater
than 1).
